<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2015-04-27 ants2015build.Rmd
ENH:  Updating with new ANTsR

## Visualize the anatomical distribution
```{r vizmorph2hide,results='hide',echo=FALSE}
betas<-antsImageClone(mask)
betavec<-abs(mylmresults$beta.t[1,])
betas[mask==1]<-betavec
SmoothImage(dim,betas,1.5,betas)
thresh<-paste(3.0,'x',max(betavec),sep='')
ofn<-paste(figpath,'vizmorph2.jpg',sep='')
```

```{r vizmorph2,results='hide'}
plotANTsImage(img,functional=list(betas),threshold=thresh,
  outname=ofn)
```

>>>>

## Visualize the anatomical distribution
```{r vizmorph2hide,results='hide',echo=FALSE}
betas<-antsImageClone(mask)
betavec<-abs(mylmresults$beta.t[1,])
betas[mask==1]<-betavec
smoothImage(betas, 1.5)
thresh<-paste(3.0,'x',max(betavec),sep='')
ofn<-paste(figpath,'vizmorph2.jpg',sep='')
```

```{r vizmorph2,results='hide'}
plot.antsImage(img,functional=list(betas),threshold=thresh,
  outname=ofn)
```
